Outline

### 2017-07-23 Outline.Rmd
added competing tech and innovation

### Comparison and contrast with competing technologies  
+ Swirl lessons
+ Anything else?

### Explain why technology is innovative
+ Coding lesson and instructions are juxtaposed with practice window, built in points and assessments to check for understanding, can integrate class with learning management systems

>>>>

### Comparison and contrast with competing technologies  
+ Swirl lessons
+ 'Try R' by Code School 
+ Anything else?

### Explain why technology is innovative
+ Coding lesson and instructions are juxtaposed with practice window, built in points and assessments to check for understanding, can integrate class with learning management systems
+ All DataCamp courses are linked through GitHub version control, making it easy for statistics educators to collaborate and reproduce code.
